Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-12-10 doc/Paper/main.tex
comments onf fig 7

      First, we have compared our fiducial power spectra, computed using contaminant deprojection, with power spectra computed without accounting for any type of contamination (i.e. estimated directly from the observed galaxy overdensity maps). This allows us to test the worst-case scenario where any source of contamination is completely ignored. The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in pink in Figure \ref{fig:cls_systematics}. In all cases we observe very small differences (smaller than $1\sigma$) between both spectra. This suggests that the level of contamination in the raw galaxy overdensity maps is small, and the linear model implemented through template deprojection is likely accurate enough to account for it.
      \begin{figure}
        \centering
        \includegraphics[width=0.49\textwidth]{figures/ndens_syst.pdf}
        \includegraphics[width=0.49\textwidth]{figures/systmask.pdf}
        \caption{{\sl Left panels:} relation between the galaxy density fluctuation ($y$ axis) and the fluctuation in different systematics ($x$-axis). In all cases $R(x)\equiv \sfrac{x}{\bar{x}}$. Results are shown for $r$-band airmass (top) and dust absorption (bottom) for the third redshift bin in the VVDS field. The data are shown in burgundy, while the solid black line shows the best-fit linear relation between both quantities. In cases where a linear relation is not appropriate (as shown here for $r$-band airmass), we mask all regions where the associated contaminant is above/below a given threshold (shown as a vertical dashed line here). {\sl Right panels:} the top panel shows our fiducial ``Sirius'' mask, with the additionally masked regions associated with high levels of contamination shown in turquoise. The bottom panel shows the alternative ``Arcturus'' bright-star mask.}
        \label{fig:ndens_syst}
      \end{figure}

>>>>

      First, we have compared our fiducial power spectra, computed using contaminant deprojection, with power spectra computed without accounting for any type of contamination (i.e. estimated directly from the observed galaxy overdensity maps). This allows us to test the worst-case scenario where any source of contamination is completely ignored. The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in pink in Figure \ref{fig:cls_systematics} (note that the different curves shown there are strongly correlated with each other). In all cases we observe very small differences (smaller than $\sim0.3\sigma$) between both spectra. This suggests that the level of contamination in the raw galaxy overdensity maps is small, and the linear model implemented through template deprojection is likely accurate enough to account for it.
      \begin{figure}
        \centering
        \includegraphics[width=0.49\textwidth]{figures/ndens_syst.pdf}
        \includegraphics[width=0.49\textwidth]{figures/systmask.pdf}
        \caption{{\sl Left panels:} relation between the galaxy density fluctuation ($y$ axis) and the fluctuation in different systematics ($x$-axis). In all cases $R(x)\equiv \sfrac{x}{\bar{x}}$. Results are shown for $r$-band airmass (top) and dust absorption (bottom) for the third redshift bin in the VVDS field. The data are shown in burgundy, while the solid black line shows the best-fit linear relation between both quantities. In cases where a linear relation is not appropriate (as shown here for $r$-band airmass), we mask all regions where the associated contaminant is above/below a given threshold (shown as a vertical dashed line here). {\sl Right panels:} the top panel shows our fiducial ``Sirius'' mask, with the additionally masked regions associated with high levels of contamination shown in turquoise. The bottom panel shows the alternative ``Arcturus'' bright-star mask.}
        \label{fig:ndens_syst}
      \end{figure}
